### 2010-04-01 papers/icfp-2010-desc/paper_desc.tex
Desc@ICFP: clean-up some \note{}s.

While sigmas-of-sigmas form a convenient \emph{semantics} for
datatypes, we have seen that it makes a poor \emph{syntax}. To
decouple these two notions, we construct an ad-hoc
\emph{universe}. This technique originates in Martin-L\"of definition
of type theory~\cite{martin-lof:itt}. It is a fruitful programming
technique in dependently-typed
languages~\cite{benke:universe-generic-prog, oury:power-of-pi}
\note{Any idea of other papers?}.  \note{Is that really a motivating
  motivation for the usage of universe construction?}  \note{pwm:
  Surely ($\EnumU$, $\EnumT$) is a useful example of universes too.
  Even if it doesn't show off their full power?}

The key idea behind universe construction is our ability to make names
by defining new types. These names are called \emph{codes}. By
defining a set of codes, we define the syntax of a language. To give
it a semantics, we \emph{interpret} these codes back into the type
theory. Hence, codes act as labels, while the type theory provides the
computational machinery. \note{Is that a good description?}

>>>>

While sigmas-of-sigmas form a convenient \emph{semantics} for
datatypes, we have seen that it makes a poor \emph{syntax}. To
decouple these two notions, we construct an ad-hoc
\emph{universe}. This technique originates in Martin-L\"of definition
of type theory~\cite{martin-lof:itt}. It is a fruitful programming
technique in dependently-typed
languages~\cite{benke:universe-generic-prog, oury:power-of-pi}.

The key idea behind universe construction is our ability to make names
by defining new types. These names are called \emph{codes}. By
defining a set of codes, we define the syntax of a language. To give
it a semantics, we \emph{interpret} these codes back into the type
theory. Hence, codes act as labels, while the type theory provides the
computational machinery.
